\documentclass[]{tufte-handout}
\usepackage{amsmath}

\title{INTG 388 - Paper \#2 }
\author{James Logan Mayfield}
\date{ Spring 2015 }

\begin{document}
\maketitle

\section{Prompt}

We don't need to look into the future to consider the ramifications of whether or not you choose to adopt a piece of AI-enhanced technology\sidenote{if you cannot find something utilizing AI, then you can get approval for non-AI based technology from the instructor} into your life.  The future is now\sidenote{sorry... had to say it}.  

You may approach this paper from one of three directions:
\begin{enumerate}
\item \textit{I would never} \newline
Identify a piece of technology you've made it a point to avoid and consider the ramifications of your choice.

\item \textit{I would totally} \newline
Identify a piece of technology that you've gladly incorporate into your life and consider the ramifications of your choice. 

\item \textit{That's just the way it is} \newline
Identify a piece of technology that you've adopted without any real conscious choice in the matter and consider the ramifications of your lack of oversight. 
\end{enumerate}

Frame your analysis and reflection in the same way we've been framing class discussions; examine the quantity and quality of control surrendered to the  technology as well as the short and long term impact of its adoption. A proper analysis must consider the reasons for and against using the technology. Your reflection should balance those reasons against your own decisions or lack thereof. As our focus is on AI-based and AI-enhanced technology, you should be certain to examine your intellectual life as well as life in general. To ground your analysis and reflection, you must seek out at least two external sources. These sources should provide perspective on the technology and the consequences of using it. Your paper must use proper citations and include a bibliography. Both should be in MLA format\sidenote{Other formats are allowed but must be approved}. All sources must be added to the group library on Zotero.


\section{Reflective Writing}

Reflection is an inward looking process. We're trying to explore what's inside us as individuals and a species. This paper is not about making a point or presenting information. It's about exploring an experience, and idea, or a possible answer to a questions and seeing how it impacts us on a personal level. We're exploring the human condition and how we make sense of it. We can think of this process in terms of three phases:
\begin{enumerate}
\item \textbf{Observation:} Students should carefully describe, explain, or notice. Their writing should make clear that they've taken some time to carefully observe. \newline
\item \textbf{Analysis:} After observing, students should then explore. They should break ideas down and put them back together. They should begin making connections between ideas encountered in the course and their own experience. They should consider what their reflection means to them intellectually, personally, and socially. \newline
\item \textbf{Deriving Implications and Meaning:} Students should offer conclusions about where the reflection has brought them. These conclusions may be partial, plural, or not fully settled, but students should be able to articulate how they think differently at the end of their reflection. They may have new ideas. They may have new understandings of old beliefs. In any case, they should articulate where they stand in relation to the reflection practiced. 
\end{enumerate}


\section{Requirements \& Logistics}

\begin{tabular}{ll}
\textsc{Due} & Before you leave for spring break  \\
\textsc{Format} & Typed. Printed. Double-spaced. Stapled. \\
\textsc{Length} & 750 - 1250 words \\
\textsc{Minimum Required External Sources} & 2
\end{tabular}

Grades are based on the quality and clarity of the writing, the appropriateness and quality of observations, the depth and sufficiency of the analysis, and the clarity and validity of the conclusions with respect to the overall reflections.  

\section{The Writing Center}

Wonderful ideas and deep reflection can be lost or ruined by muddled writing.  I grew most as a writer when I cared deeply about the things I was writing and didn't want there to be any uncertainty on the part of my readers. Perhaps more than other forms or writing, reflective writing is ultimately a reflection of ourselves. You should want to put your best word forward when it's you on the page. Writing well is hard. It takes practice. I requires help. I encourage \textit{all} of you to take this opportunity to step up your writing game. The writing center is here to help you. They're awesome. Don't wait until my grade to get feedback on the quality and clarity of your writing.  
\begin{quote}
The Monmouth College Writing Center offers unlimited, free peer tutoring sessions for students at MC.  Peer writing tutors work with writers from any major, of any writing ability, on any type of writing assignment, and at any stage of their writing processes, from planning to drafting to revising to editing.  We are located on the 3rd floor of the Mellinger Teaching and Learning Center, and we are open Sunday-Thursday 7-10pm and Monday-Thursday 3-5pm on a first-come, first-served basis.  No appointment necessary!  International students can sign up to work with the same writing tutor for a weekly session. Learn more about the Writing Center at our website: \url{http://blogs.monm.edu/writingatmc/writing-center/}
\end{quote}




\end{document}