\documentclass[]{tufte-handout}

\title{INTG 388 \\ Paper \#4 }
%\author{ James Logan Mayfield }
\date{ Fall 2017 }

\begin{document}
\maketitle

\section{Prompt}

For your final paper you will use Philip K Dick's novel\citep{dick_androids_2008} and McGrath's article\citep{mcgrath_religion_2011} as guides into the quagmire that is consciousness and strong AI\@. For this paper you need to reflect on the problems and promises for strong AI or machine persons. Is the pursuit of strong AI the right thing for humanity? If so, what is the right path forward towards strong AI\@? If not, why not? What would the existence of strong AI mean \textit{for you personally?} What if we could prove strong AI were impossible, what would that mean to you? As always keep your reflection grounded in specific observations and analysis pulled from your sources and your own experiences. When seeking out additional sources, make efforts to balance the ideas of P.K.D. and McGrath with alternative views and ideas. Note that this paper is longer than your previous papers. This should allow you to further develop your ideas with such a notoriously tricky subject.

\section{Requirements \& Logistics}

\begin{tabular}{ll}
\textsc{Due} & \textbf{Electronically via turnitin.com} on   \\
\textsc{Format} & Typed. Double-spaced. \\
\textsc{Length} & \textbf{1500--2000 words} \\
\textsc{Minimum Required External Sources} & 4 (Book,Paper,+2)
\end{tabular}


\vspace{.1in}

Detailed instructions for electronic submission will be handed out in class. Grades are based on the quality and clarity of the writing, the appropriateness and quality of observations, the depth and sufficiency of the analysis, and the clarity and validity of the conclusions with respect to the overall reflections. Be sure to review \textit{On Reflection and Reflective Writing}\sidenote{\url{https://jlmayfield.github.io/teaching/INTG335/intg335-reflection.pdf}} if needed.

\section{The Writing Center}

Wonderful ideas and deep reflection can be lost or ruined by muddled writing.  I grew most as a writer when I cared deeply about the things I was writing and didn't want there to be any uncertainty on the part of my readers. Perhaps more than other forms or writing, reflective writing is ultimately a reflection of ourselves. You should want to put your best word forward when it's you on the page. Writing well is hard. It takes practice. I requires help. I encourage \textit{all} of you to take this opportunity to step up your writing game. The writing center is here to help you. They're awesome. Don't wait until my grade to get feedback on the quality and clarity of your writing.
\begin{quote}
The Monmouth College Writing Center offers unlimited, free peer tutoring sessions for students at MC\@.  Peer writing tutors work with writers from any major, of any writing ability, on any type of writing assignment, and at any stage of their writing processes, from planning to drafting to revising to editing.  We are located on the 3rd floor of the Mellinger Teaching and Learning Center, and the Writing Center is open Sun-Thurs 7--10pm, and Mon-Thurs 3--5pm on a first-come, first-served basis.  No appointment necessary!  International students can sign up to work with the same writing tutor for a weekly session. Learn more about the Writing Center at our website: \url{http://blogs.monm.edu/writingatmc/writing-center/}
\end{quote}

\bibliographystyle{plainnat}
\bibliography{intg335-end.bib}
\end{document}
