\documentclass[]{tufte-handout}


\title{INTG 388 - The End is Near }
\author{James Logan Mayfield}
\date{ Spring 2015 }

\begin{document}
\maketitle

\section{ \textit{Do Androids Dream of Electric Sheep?} }

We'll spend the rest of our time on \textit{Do Android's Dream of Electric Sheep?}\cite{dick_androids_2008} by Philip K Dick. Our goal is to bring everything we've been doing together through this novel and finally get into issues of consciousness and strong AI. To further motivate your reading and get you thinking towards the final paper, I want your final five journal entries to be short reflections about specific readings. The follow chart tells when chapters are due and which chapters should be read by which dates and which chapters should be the object of reflection for which journal entries. 

\begin{center}
\begin{tabular}{llll}
Date & Chapters Due & Total Pages & Journal \\ \hline
4/19 & 1-3,4,5 & 58 & 1 (due this day)\\
4/22 & 6-7 & 23 & 2 \\
4/24 & 8 & 13 & 2 \\
4/27 & 9-11,12 & 48 & 3 \\
4/29 & 13-15 & 39 & 4 (2 \& 3 due)\\
5/1 & 16-17 & 19 & 5 \\
5/4 & 18-19,20-22 & 44 &  (4 \& 5 due)
\end{tabular}
\end{center}

\subsection{Journals}

The first journal should be focus on your understanding and impression of the world in which our novel takes place. All subsequent journals should be reflections on how, specifically, the content of the reading relates to and informs everything we've been doing so far. 

\section{Final Presentation}

On May 12 from 6:30-9:30pm we'll be doing our on personal version of edge.org's \textit{What Do You Think About Machines That Think?}\sidenote{\url{http://edge.org/annual-question/what-do-you-think-about-machines-that-think}}.  You'll have \textit{five minutes} to read or present your final reflective journal entry for the entire course. The prompt is the same as edge.orgs. I recommend you spend some time looking at the submissions there in addition to reflection on the course as whole. You must write this entry and bring a printed copy for submission on 5/12\sidenote{If you intended to read your entry, bring a copy to read and a copy to submit}.  

\section{Paper 4 Preview}

You'll get your final paper prompt soon. It will be \textit{due by midnight 5/6} and submitted electronically through turnitin.com. The topic will, broadly speaking, be strong AI and you'll be required to use the final novel as one of your sources. 

\bibliographystyle{plain}
\bibliography{intg388-end.bib}
\end{document}	