\documentclass[nobib]{tufte-handout}
\usepackage{amsmath}

\title{INTG 335 \\ Paper \#1 }
%\author{James Logan Mayfield }
\date{ Fall 2017 }

\begin{document}
\maketitle
\thispagestyle{empty}

\subsection*{The Prompt}

The era of human supremacy in games of intelligence and strategy appears to be coming to an end. The classics like Checkers, Chess, and Go have fallen to AI with seemingly superhuman playing capabilities. Games of chance like Poker are beginning to fall as well. Major developers of AI such as DeepMind are having great success in the realm of video games as well. None the less, humans continue to dedicate their lives to the pursuit of excellence in these games. In your first paper you will explore how, if at all, these pursuits have changed in a post-AI-supremacy world.

%% Refine/Edit/Narrow/Focus these questions
Has the pursuit of excellence in games lost or gained value? Does it matter that our benchmarks of the highest excellence and intelligence are machines and not human beings?  Does the existence of a super-human player and in some cases a perfect player\sidenote{i.e. Chinook and the solution to Checkers} make playing a game well more or less meaningful? More generally, what if anything, does it say about our own intelligence if machines can beat us at our own games? It's just a game, right?

%% Parameters -


\section{Requirements \& Logistics}

\begin{tabular}{ll}
\textsc{Due} &  \\
\textsc{Format} & Typed. Printed. Double-spaced. Stapled. \\
\textsc{Length} & 750--1250 words \\
\textsc{Min. Sources} & 3
\end{tabular}
\vspace{.25in}

Grades are based on the quality and clarity of the writing, the appropriateness and quality of observations, the depth and sufficiency of the analysis, and the clarity and validity of the conclusions with respect to the overall reflections. Be sure to review \textit{On Reflection and Reflective Writing}\sidenote{\url{https://jlmayfield.github.io/teaching/INTG335/intg335-reflection.pdf}} if needed.

\section{The Writing Center}

Wonderful ideas and deep reflection can be lost or ruined by muddled writing.  I grew most as a writer when I cared deeply about the things I was writing and didn't want there to be any uncertainty on the part of my readers. Perhaps more than other forms or writing, reflective writing is ultimately a reflection of ourselves. You should want to put your best word forward when it's you on the page. Writing well is hard. It takes practice. I requires help. I encourage \textit{all} of you to take this opportunity to step up your writing game. The writing center is here to help you. They're awesome. Don't wait until my grade to get feedback on the quality and clarity of your writing.
\begin{quote}
The Monmouth College Writing Center offers unlimited, free peer tutoring sessions for students at MC\@.  Peer writing tutors work with writers from any major, of any writing ability, on any type of writing assignment, and at any stage of their writing processes, from planning to drafting to revising to editing.  We are located on the 3rd floor of the Mellinger Teaching and Learning Center, and the Writing Center is open Sun-Thurs 7--10pm, and Mon-Thurs 3--5pm on a first-come, first-served basis.  No appointment necessary!  International students can sign up to work with the same writing tutor for a weekly session. Learn more about the Writing Center at our website: \url{http://blogs.monm.edu/writingatmc/writing-center/}
\end{quote}

\end{document}
