\documentclass[]{tufte-handout}

\title{INTG 388 - Final }
\author{}
\date{ Spring 2016 }

\begin{document}
\maketitle

During the final period you'll submit two things: some responses to three general assessment questions about reflections and INTG along with a final journal entry. The journals will then be presented to the class. These two things account for your final presentation grade (5\% of your total grade). If you fail to turn in the assessment question responses, then you'll receive a zero for the presentation. If you turn the responses in, then your presentation grade is based off written journal and its presentation.  The journal does not count towards your journal grade, just the final presentation grade.  

\section*{Final Journal Presentation}

In 2015, the website \url{http://www.edge.org} asked leaders and thinkers the question ``What do you think about machines that think?''\sidenote{\url{https://www.edge.org/annual-question/what-do-you-think-about-machines-that-think}}. The essays that resulted were published and made available as a book and online. For the final presentation you'll be writing a final journal entry and reading it to the class. The prompt for this journal is the same question edge.org asked: \textit{What do you think about machines that think?}.  You may interpret this question however you wish and respond in whatever way you find appropriate so long as the response is personal and reflective in nature. 


\section*{Common Reflections Assessment Questions}

Answer the following.  
\begin{enumerate}
\item How did the final paper help to build the skill of critical reflection? How did the reflection paper help you to reflect on and articulate your own answers to a significant question of meaning and value?

\item Briefly explain what you take to be the most important thing that you learned from each of the following courses: Introduction to Liberal Arts, Global Perspectives and Reflections. Do you see that what you've learned in these courses fits together in some way? If so, how? If not, why not?

\item How has what you've learned in this Reflections course prepared you for a capstone course in Citizenship? What kind of Citizenship course might you be looking for and why?
\end{enumerate}



\end{document}	