\documentclass[nobib]{tufte-handout}

\title{INTG 388 - Robot \& Frank Worksheet}
\author{}
\date{ Spring 2016 }


\begin{document}
\maketitle
\thispagestyle{empty} 

\begin{center}
\textbf{Turn in after we finish the film Wednesday}
\end{center}

We won't be able to discuss the film \textit{Robot and Frank} until we return, so to be sure you have something to jog your memory when you return, you're going to fill out this worksheet as you watch the film. We're looking for observations that cut across all three of the major topics we've covered in this course thus far.

\begin{itemize}
\item AI and Human Intellect:  How do AI in the film cause people to re-evaluate the ways in which they use their intellect?
\item AI at the Wheel: What happens when characters in the film let the machines do things for them and what does that say, if anything, about their priorities and values? 
\item Relationships with AI: How do the characters in the film interact with AI? Is is a relationship of projection or engagement? How do AI interact with each other and how does that compare to human-AI interactions?
\end{itemize}

Observations should deal with specific characters and specific encounters. If you start to see themes emerging, then make note of them only after you've seen several scenes that draw upon the larger theme. We'll ferret out the big picture later.  For now you need to look at moment to moment details.

\newpage \thispagestyle{empty} 
\section*{AI and Human Intellect}
\newpage \thispagestyle{empty} 
\section*{AI at the Wheel}
\newpage \thispagestyle{empty} 
\section*{Relationships with AI}

\end{document}