\documentclass[nobib]{tufte-handout}

\title{INGT 335 --- Artificial Intelligence \\ Journal 1}
\author{}
\date{ Fall 2017 }

\begin{document}
\maketitle


The goal for your first journal is to sketch out ideas for the different parts of a reflection.  This is a pre-writing type of exercise.

\subsection{The Assignment}

In class you were placed into groups in order to brainstorm different tasks that do and do not require intelligence. You should now now reflect on that experience by working through the following:

\begin{enumerate}
  \item \textit{Know where you started.} Prior to today's discussion, what value did you place on your own intelligence? What about others? How about your intelligence relative to other's intelligence? What about relative to other aspects of your being (i.e. your health and fitness, your empathy, etc.)?

  \item \textit{Observe something relevant.} What's your take on the intelligence spectrum we constructed? What stands out? Do you disagree with any of it? Were you surprised by it?  Be as specific as possible in your observations and do not be afraid to look deeply at some small piece of the spectrum. Your goal is to understand and explain what you're seeing.  Don't argue for or against something, simply seek to understand what's in front of you.

  \item \textit{Analyze the impact of what your observed with respect to where you started.}  Now that you understand what's in front of you, closely examine how it impacts you personally and how it interacts with your prior perspective on intelligence. If something surpsied you, why? If what you saw agrees with your prior views on intelligence, what was missing that might have caused you to question those views?  What experiences and ideas have led you to disgree with something that you saw? The goal here is to closely examine how what you've observed interacts your views prior to the observation.

  \item \textit{Come to \textit{a} conclusion about how you've changed.} This last part is arguably the most important as the conclusion you draw from your analysis becomes our version of a thesis statement.  What impact has placing your own views on intelligence against those of others had on you? Do you see things differently? If so, how? If not, why? The real enemy here is some sense that you must answer some great mystery or that your conclusion is a life long committment. Specificity is your friend.

\end{enumerate}



\end{document}
