\documentclass[nobib]{tufte-handout}
\usepackage{amsmath}

\title{INTG 335 \\ Paper \#2 }
%\author{ James Logan Mayfield }
\date{ Fall 2017 }

\begin{document}
\maketitle

\section{Prompt}

We've now turned our attention from games to tasks and skills that drive aspects of everyday life. What seems to be a recurring theme is the continued supremacy of AI\@. Key tasks in medicine and science are increasingly being done by machines. Self-driving cars are better drivers than humans and as a result will save lives. Automated factories are safer, more efficient, and will lead to cheaper goods. AI are even able to produce works of art comparable to human artists and can be used as a means to extend the human artist's capabilities. In this paper you'll push back, or not, on the rise of the machines in your day-to-day life.

%Refine Questions
Look at the various places you encounter AI in your life and the kinds of things you allow the machine to do for you. Where do you draw the line? When, if at all, do you accept sub-optimal results produced by humans or when do you demand that you carry out certain tasks rather than an AI\@? When does ethics or aesthetics trump efficiency and ease of use? Be certain to ground your reflection in the here and now. Do not look at technologies that are not yet available and imagine future choices you must make, but examine and reflect upon the choices about your use of AI that you are making right now.

\section{Requirements \& Logistics}

\begin{tabular}{ll}
\textsc{Due} & \textbf{Monday 10/9}  \\
\textsc{Format} & Typed. Printed. Double-spaced. Stapled. \\
\textsc{Length} & 750--1250 words \\
\textsc{Min. Sources} & 3
\end{tabular}
\vspace{.25in}

Grades are based on the quality and clarity of the writing, the appropriateness and quality of observations, the depth and sufficiency of the analysis, and the clarity and validity of the conclusions with respect to the overall reflections. Be sure to review \textit{On Reflection and Reflective Writing}\sidenote{\url{https://jlmayfield.github.io/teaching/INTG335/intg335-reflection.pdf}} if needed.

\section{The Writing Center}

Wonderful ideas and deep reflection can be lost or ruined by muddled writing.  I grew most as a writer when I cared deeply about the things I was writing and didn't want there to be any uncertainty on the part of my readers. Perhaps more than other forms or writing, reflective writing is ultimately a reflection of ourselves. You should want to put your best word forward when it's you on the page. Writing well takes practice. It requires help. I encourage \textit{all} of you to take this opportunity to step up your writing game. The writing center is here to help you. They're awesome. Don't wait until my grade to get feedback on the quality and clarity of your writing.
\begin{quote}
  The Writing Center offers unlimited, free peer tutoring sessions for Monmouth College students.  Peer writing tutors are trained to work with writers from any major, of any writing ability, on any type of writing assignment, and at any stage of their writing processes, from planning to drafting to revising to editing.  Peer speech tutors are also available on a limited basis to assist student speakers at any point in the process of designing a speech – from outlining to delivery.  The Writing Center is  located on the 3rd floor of the Mellinger Teaching and Learning Center, and is open Sunday-Thursday 7--10pm and Monday-Thursday 3--5pm on a first-come, first-served basis.  No appointment necessary!
\end{quote}

\end{document}
